---
title: "First R Markdown"
author: Zachary Katz
date: 2021-09-16
output: github_document

---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
library(tidyverse)
samp=rnorm(500)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Let's write a new code chunk.

This code chunk imports the `tidyverse`, creates a data frame, and makes a histogram.

```{r, message=FALSE}
set.seed(1234)

plot_df <- 
      tibble(
            x = rnorm(1000, sd = .5),
            y = 1 + 2 * x + rnorm(1000)
      )
plot_df

ggplot(plot_df, aes(x=x)) + geom_histogram()
```

## Learning Assessment

This is the learning assessment from the course website. Instructions are as follows:
_Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?/_

```{r, learning_assessment}
set.seed(12)
learning_assessment_df <- 
      tibble(
            x = rnorm(500, mean = 1),
            y = x > 0,
            abs_x = abs(x)
      )

ggplot(learning_assessment_df, aes(x=abs_x)) + geom_histogram()

median_samp = median(pull(learning_assessment_df, abs_x))
```
The median of the variable containing absolute values is  `r round(median_samp, digits=2)`.

* Also, this is a practice bullet point.
